---
title: "Seine_02: Run a semi-distributive GR model network"
author: "David Dorchies"
vignette: >
  %\VignetteIndexEntry{Seine_02: Run a semi-distributive GR model network}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load libraries

```{r}
library(airGRiwrm)
```


## Load parameters of GR4 run-off model

### Loading network and time series data

Run `vignette("01_First_network", package = "airGRiwrm")` before this one in order to create the Rdata file loaded below:

```{r}
load("_cache/V01.RData")
```

### Loading

Data comes from calibration of ClimAware project with naturalised flows.

```{r}
ClimAwareParams <- read.csv(
  file = paste0(seinebasin::url_data, "?p=/climaware_hydro/Ident_NAT_P0P0.txt&dl=1")
)

ClimAwareParams
```

The lag $\tau_0$ and route $K_0$ parameters of TGR are expressed as time delay in hours corresponding to the delay time between the farest upstream inlet and the outlet of the sub-basin.
Almost all sub basin has only a lag parameter. The only exception is for La Marne à Noisiel (NOISI_17) that has a routing parameter which can be approximated to a single lag parameter equals to $\tau_0 + K_0$.

This lag parameter has to be converted in a speed in m/s used in the **airGR** lag model:

```{r}
# Convert TGR routing parameter into speed
params <- merge(griwrm, ClimAwareParams, by.x = "id", by.y = "id_sgl")

ParamClimAware <- sapply(griwrm$id, function(id) {
  nodeParam <- ClimAwareParams[ClimAwareParams$id_sgl == id,]
  # Record hydrological model parameters
  Param <- unlist(nodeParam[c("S", "IGF", "KR", "T")])
  # Add lag model parameter if upstream nodes exist
  UpstrNodes <- which(griwrm$down == id & !is.na(griwrm$down))
  if(length(UpstrNodes) > 0) {
    maxLength <- max(griwrm$length[UpstrNodes])
    Param <- c(
      maxLength * 1000 / ((nodeParam$Tau0 + nodeParam$K0) * 3600),
      Param
    )
  }
  return(Param)
})

```

## GriwmRunOptions object

The `CreateRunOptions()` function allows to prepare the options required to the `RunModel()` function.

The user must at least define the following arguments:

* InputsModel: the associated input data
* IndPeriod_Run: the period on which the model is run


```{r}
IndPeriod_Run <- seq(
  which(InputsModel[[1]]$DatesR == (InputsModel[[1]]$DatesR[1] + 365*24*60*60)), # Set aside warm-up period
  length(InputsModel[[1]]$DatesR) # Until the end of the time series
)
```

The warmup period could also be defined as is:

```{r}
IndPeriod_WarmUp = seq(1,IndPeriod_Run[1]-1)
```



```{r}
RunOptions <- CreateRunOptions(
  InputsModel = InputsModel,
  IndPeriod_WarmUp = IndPeriod_WarmUp,
  IndPeriod_Run = IndPeriod_Run
)
```



## Run the SD model for the whole basin

```{r}
OutputsModelsClimAware <- RunModel(
  InputsModel,
  RunOptions = RunOptions,
  Param = ParamClimAware
)
```

## Save data for next vignettes

```{r}
save(RunOptions, ParamClimAware, IndPeriod_Run, file = "_cache/V02.RData")
```

## Plot the result for each basin

```{r, fig.height = 5, fig.width = 8}
plot(OutputsModelsClimAware, Qobs = Qobs[IndPeriod_Run,])
```






