---
title: "Seine_02: Run a semi-distributed GR model network"
author: "David Dorchies"
vignette: >
  %\VignetteIndexEntry{Seine_02: Run a semi-distributed GR model network}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The aim of this vignette is to run the simulation of the semi-distributed model of the Seine River with naturalized flows.

## Load libraries

```{r library}
library(airGRiwrm)
```


## Load parameters of the GR4J runoff model

### Loading network and time series data

It is necessary to run the `vignette("01_First_network", package = "airGRiwrm")` before this one in order to create the Rdata file loaded below:

```{r load}
load("_cache/V01.RData")
```

### Loading

GR4J parameters come from a calibration realized during the ClimAware project using naturalized flows.

```{r ClimAwareParams}
library(seinebasin)
data(ClimAwareParams)
names(ClimAwareParams) <- c("id_sgl", "Tau0", "K0", "X1", "X2", "X3", "X4", "NashId")
ClimAwareParams
```

The lag $\tau_0$ and routing $K_0$ parameters of TGR are expressed as time delay in hours corresponding to the delay time between the farthest upstream inlet and the outlet of the sub-basin.
Almost all sub basins have a routing parameter equal to 0. The only exception is for La Marne à Noisiel (NOISI_17) that has a routing parameter that can be approximated to a single lag parameter equal to $\tau_0 + K_0$.

This lag parameter has to be converted in a speed in m/s used in the **airGR** lag model:

```{r ParamClimAware}
# Convert TGR routing parameter into speed
params <- merge(griwrm, ClimAwareParams, by.x = "id", by.y = "id_sgl")

ParamClimAware <- sapply(griwrm$id, function(id) {
  nodeParam <- ClimAwareParams[ClimAwareParams$id_sgl == id,]
  # Record hydrological model parameters
  Param <- unlist(nodeParam[c("X1", "X2", "X3", "X4")])
  # Add lag model parameter if upstream nodes exist
  UpstrNodes <- which(griwrm$down == id & !is.na(griwrm$down))
  if (length(UpstrNodes) > 0) {
    maxLength <- max(griwrm$length[UpstrNodes])
    Param <- c(
      maxLength * 1000 / ((nodeParam$Tau0 + nodeParam$K0) * 3600),
      Param
    )
  }
  return(Param)
})

```

## GriwmRunOptions object

The `CreateRunOptions()` function allows to prepare the options required by the `RunModel()` function.

The user must at least define the following arguments:

* InputsModel: the associated input data
* IndPeriod_Run: the period on which the model is run


```{r IndPeriod_Run}
IndPeriod_Run <- seq(
  which(InputsModel[[1]]$DatesR == (InputsModel[[1]]$DatesR[1] + 365*24*60*60)), # Set aside a one-year period for warm up
  length(InputsModel[[1]]$DatesR) # Until the end of the time series
)
```

We define the (optional but recommended) warm up period as a one-year period before the run period:

```{r IndPeriod_WarmUp}
IndPeriod_WarmUp <- seq(1, IndPeriod_Run[1] - 1)
```



```{r CreateRunOptions}
RunOptions <- CreateRunOptions(
  InputsModel,
  IndPeriod_WarmUp = IndPeriod_WarmUp,
  IndPeriod_Run = IndPeriod_Run
)
```



## Run the SD model for the whole basin

```{r RunModel}
OutputsModelsClimAware <- RunModel(
  InputsModel,
  RunOptions = RunOptions,
  Param = ParamClimAware
)
```

## Plot the result for each basin

We plot the simulated discharges against the naturalized ones.

```{r plot, fig.height = 5, fig.width = 8}
data(QNAT)
plot(OutputsModelsClimAware, Qobs = Qnat[IndPeriod_Run,])
```

## Save data for next vignettes

```{r save}
save(RunOptions, ParamClimAware, IndPeriod_Run, file = "_cache/V02.RData")
```






