---
title: "Seine_03: Calibration of a semi-distributed GR model network"
author: "David Dorchies"
vignette: >
  %\VignetteIndexEntry{Seine_03: Calibration of a semi-distributed GR model network}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The aim of this vignette is to perform a first calibration of the semi-distributed hydrological model, using naturalized discharge.

## Loading libraries, network and time series data

Run `vignette("01_First_network", package = "airGRiwrm")` and `vignette("02_First_run", package = "airGRiwrm")` before this one in order to create the Rdata files loaded below:

```{r load}
library(airGRiwrm)
load("_cache/V01.RData")
load("_cache/V02.RData")
library(seinebasin)
data(QNAT)
```

## InputsCrit object

We need then to prepare the InputsCrit object that is necessary to define the calibration objective function. We chose here the KGE' criterion:

```{r CreateInputsCrit}
InputsCrit <- CreateInputsCrit(
  InputsModel = InputsModel,
  FUN_CRIT = ErrorCrit_KGE2,
  RunOptions = RunOptions,
  Obs = Qnat[IndPeriod_Run,]
)
str(InputsCrit)
```

## GRiwrmCalibOptions object

```{r CreateCalibOptions}
CalibOptions <- CreateCalibOptions(InputsModel)
str(CalibOptions)
```

## Calibration

The optimization (i.e. calibration) of parameters can now be performed:

```{r Calibration}
OutputsCalib <- Calibration(InputsModel, RunOptions, InputsCrit, CalibOptions)
```

## Run the GR4J model with parameters obtained from the Michel calibration

Now that the model is calibrated, we can run it with the optimized parameter values:

```{r RunModel}
ParamMichel <- extractParam(OutputsCalib)

OutputsModels <- RunModel(
  InputsModel,
  RunOptions = RunOptions,
  Param = ParamMichel
)
```

## Plot the result for each basin

```{r plot, fig.height = 5, fig.width = 8}
plot(OutputsModels, Qobs = Qnat[IndPeriod_Run,])
```

## Save calibration data for next vignettes

```{r save}
save(ParamMichel, file = "_cache/V03.RData")
```
