---
title: "Seine_06: Simulate naturalized flows with a model network calibrated with influenced flows"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Seine_06: Simulate naturalized flows with a model network calibrated with influenced flows}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
bibliography: seinebasin.bib
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r library}
library(airGRiwrm)
library(seinebasin)
```

This vignette is an example of flow naturalisation by modelling [@terrierStreamflowNaturalizationMethods2020].

By using the model calibrated with influenced flow on the Marne River, it's now possible to model naturalised flows by dropping the connections to the Marne reservoir from the model. 

## Set the data

Loading naturalised data and influenced flow calibration:

```{r load}
# Input data for the model
load("_cache/V01.RData")
# Calibration in influenced flows
load("_cache/V05.RData")
```

Remove lag parameter in `StDIZ_04` station because there is no longer upstream node on it.

```{r Param}
Param6 <- Param5
Param6$STDIZ_04 <- Param6$STDIZ_04[-1]
```


Remove extra items from global configuration

```{r griwrm4}
selectedNodes <- c("STDIZ_04", "LOUVE_19", "VITRY_25", "CHALO_21", "MONTR_18", "NOISI_17")
griwrm4 <- griwrm[griwrm$id %in% selectedNodes,]
griwrm4[griwrm4$id == "NOISI_17", c("down", "length")] = NA # Downstream station instead of PARIS_05
DiagramGRiwrm(griwrm4)
```

Generate `GRiwrmInputsModel` object

```{r CreateInputsModel}
data(QNAT)
InputsModel4 <- CreateInputsModel(griwrm4, DatesR, Precip, PotEvap, Qnat)
```

## GriwmRunOptions object


```{r IndPeriod_Run}
IndPeriod_Run <- seq(366, length(DatesR)) # Until the end of the time series
```

The warmup period could also be defined as is:

```{r IndPeriod_WarmUp}
IndPeriod_WarmUp = seq(1,IndPeriod_Run[1]-1)
```



```{r CreateRunOptions}
RunOptions <- CreateRunOptions(
  InputsModel = InputsModel4,
  IndPeriod_WarmUp = IndPeriod_WarmUp,
  IndPeriod_Run = IndPeriod_Run
)
```

## Run model with Michel calibration

```{r RunModel}
OutputsModels4 <- RunModel(
  InputsModel4,
  RunOptions = RunOptions,
  Param = Param6
)
```

## Compare simulated naturalised flow with the ones given by EPTB SGL

```{r plot, fig.height = 5, fig.width = 8}
htmltools::tagList(lapply(
  names(OutputsModels4),
  function(x) {
    plot(OutputsModels4[[x]], Qobs = Qnat[IndPeriod_Run,x] , main = x)
  }
))
```

# References
