---
title: 'Tutorial: structuration of a semi-distributive GR model'
author: "David Dorchies"
vignette: >
  %\VignetteIndexEntry{Tutorial: structuration of a semi-distributive GR model}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
bibliography: airGRiwrm.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(airGRiwrm)
```

The package 'airGRiwrm' is a modeling tool for integrated water resource management based on the package 'airGR' package @coron_airgr_2020.

In a semi-distributive model, the catchment is divided into several sub-catchments. Each sub-catchment is an hydrological entity where a runfall-runoff model produces a flow time series at the outlet of the sub-catchment. Then a hydraulic link is set between sub-catchment outlets to model the flow at the outlet of the whole catchment. The aim of 'airGRiwrm' is to organise the structure and schedule the execution of the hydrological and hydraulic sub-models contained in the semi-distributive model.

## Description of the example used in this tutorial

The example of this tutorial takes place on the Severn River in United Kingdom. The data set comes from the CAMEL GB database @coxon_catchment_2020.

```{r}
data(Severn)
Severn$BasinsInfo
```

## Semi-distributive network description

Create the GRiwrm object which lists the nodes and describes the network diagram. It's a data.frame of class `GRiwrm` with specific column names:

- `id`: the identifier of the node in the network.
- `down`: the identifier of the next hydrological node downstream.
- `length`: hydraulic distance to the next hydrological downstream node (m).
- `model`: Name of the hydrological model used (E.g. "RunModel_GR4J"). `NA` for other type of node.
- `area`: Area of the sub-catchment (km<sup>2</sup>). Used for hydrological model such as GR models. `NA` if not used.

`GRiwrm` function helps to rename the columns of the dataframe and assign the variable classes.

```{r}
nodes <- Severn$BasinsInfo[, c("gauge_id", "downstream_id", "distance_downstream", "area")]
nodes$distance_downstream <- nodes$distance_downstream * 1000 # Conversion km -> m
nodes$model <- "RunModel_GR4J"
# Generate the GRiwrm object
griwrm <- GRiwrm(nodes, list(id = "gauge_id", down = "downstream_id", length = "distance_downstream"))
griwrm
```

The diagram of the network structure is represented below with in blue the upstream nodes with a GR4J model and in green the intermediate nodes with an SD (GR4J + LAG) model.

```{r fig.height = 7, fig.width = 8}
DiagramGRiwrm(griwrm)
```



## Observation time series

Observations (precipitation, potential evapotranspiration and flows) should be formatted in separated data.frame with one column of data per sub-catchment.

```{r}
BasinsObs <- Severn$BasinsObs
str(BasinsObs)
```


```{r, warning=FALSE, message=FALSE}

DatesR <- BasinsObs[[1]]$DatesR

Precip <- cbind(sapply(BasinsObs, function(x) {x$precipitation}))
PotEvap <- cbind(sapply(BasinsObs, function(x) {x$peti}))
Qobs <- cbind(sapply(BasinsObs, function(x) {x$discharge_spec}))
```

## Generate the GRIWRM InputsModel object

The GRIWRM InputsModel object is a list of airGR InputsModel. The identifier of the sub-basin is used as key in the list which is ordered from upstream to downstream.

The airGR CreateInputsModel function is extended in order to handle the griwrm object which describe the basin diagram:


```{r}
InputsModel <- CreateInputsModel(griwrm, DatesR, Precip, PotEvap, Qobs)
```



## Save data for next vignettes

```{r}
dir.create("_cache", showWarnings = FALSE)
save(griwrm, Qobs, InputsModel, file = "_cache/V01.RData")
save(griwrm, DatesR, Precip, PotEvap, Qobs, file = "_cache/V01b.RData")
```

# References
