---
title: 'Tutorial: structure of a semi-distributive GR model'
author: "David Dorchies"
vignette: >
  %\VignetteIndexEntry{Tutorial: structure of a semi-distributive GR model}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
bibliography: airGRiwrm.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(airGRiwrm)
```

The package **airGRiwrm** is a modeling tool for integrated water resource management based on the package **airGR** package [See @coronSuiteLumpedGR2017].

In a semi-distributive model, the catchment is divided into several sub-catchments. Each sub-catchment is an hydrological entity where a runfall-runoff model produces a flow time series at the outlet of the sub-catchment. Then a hydraulic link is set between sub-catchment outlets to model the flow at the outlet of the whole catchment. The aim of **airGRiwrm** is to organise the structure and schedule the execution of the hydrological and hydraulic sub-models contained in the semi-distributive model.

In this vignette, we show how to prepare observation data for the model.

## Description of the example used in this tutorial

The example of this tutorial takes place on the Severn River in United Kingdom. The data set comes from the CAMEL GB database [See @coxonCatchmentAttributesHydrometeorological2020].

```{r}
data(Severn)
Severn$BasinsInfo
```

## Semi-distributive network description

The semi-distributive model comprises nodes. Each node identified by an ID represents a location where water is injected to or withdrawn from the network.

The description of the topology consists in giving the first ID located downstream each node and the distance between these two nodes. These value are `NA` for the last downstream node.

A hydrological model can be defined for each node and in that case the area related to the node should be filled.

Here below, we constitute a `data.frame` bringing together all this information for the tutorial example:

```{r}
nodes <- Severn$BasinsInfo[, c("gauge_id", "downstream_id", "distance_downstream", "area")]
nodes$distance_downstream <- nodes$distance_downstream
nodes$model <- "RunModel_GR4J"
```

The network description consists in a `GRiwrm` object which lists the nodes and describes the network diagram. It's a `data.frame` of class `GRiwrm` with specific column names:

- `id`: the identifier of the node in the network.
- `down`: the identifier of the next hydrological node downstream.
- `length`: hydraulic distance to the next hydrological downstream node (m).
- `model`: Name of the hydrological model used (E.g. "RunModel_GR4J"). `NA` for other type of node.
- `area`: Area of the sub-catchment (km<sup>2</sup>). Used for hydrological model such as GR models. `NA` if not used.


The `GRiwrm` function helps to create an object of class `GRiwrm`. It renames the columns of the `data.frame`.

```{r}
griwrm <- GRiwrm(nodes, list(id = "gauge_id", down = "downstream_id", length = "distance_downstream"))
griwrm
```

The diagram of the network structure is represented below with in blue the upstream nodes with a GR4J model and in green the intermediate nodes with an SD (GR4J + LAG) model.

```{r diagram}
DiagramGRiwrm(griwrm)
```



## Observation time series

Observations (precipitation, potential evapotranspiration and flows) should be formatted in separated data.frame with one column of data per sub-catchment.

```{r}
BasinsObs <- Severn$BasinsObs
str(BasinsObs)
```


```{r, warning=FALSE, message=FALSE}

DatesR <- BasinsObs[[1]]$DatesR

PrecipTot <- cbind(sapply(BasinsObs, function(x) {x$precipitation}))
PotEvapTot <- cbind(sapply(BasinsObs, function(x) {x$peti}))
Qobs <- cbind(sapply(BasinsObs, function(x) {x$discharge_spec}))
```

This meteorological data are mean precipitation and PE for each basin. The model needs mean precipitation and PE at sub-basin scale. The function `ConvertMeteoSD` calculates these values for downstream sub-basins:

```{r}
Precip <- ConvertMeteoSD(griwrm, PrecipTot)
PotEvap <- ConvertMeteoSD(griwrm, PotEvapTot)
```


## Generate the GRiwrmInputsModel object

The `GRiwrmInputsModel` object is a list of **airGR** `InputsModel`. The identifier of the sub-basin is used as key in the list which is ordered from upstream to downstream.

The **airGR** `CreateInputsModel` function is extended in order to handle the `GRiwrm` object which describe the basin diagram:


```{r}
InputsModel <- CreateInputsModel(griwrm, DatesR, Precip, PotEvap, Qobs)
```



## Save data for next vignettes

```{r}
getwd()
dir.create("cache", showWarnings = FALSE)
save(griwrm, Qobs, InputsModel, file = file.path(tempdir(), "V01.RData"))
save(griwrm, DatesR, Precip, PotEvap, Qobs, file = file.path(tempdir(), "V01b.RData"))
```

# References
