---
title: 'Tutorial: structuration of a semi-distributive GR model'
author: "David Dorchies"
vignette: >
  %\VignetteIndexEntry{Tutorial: structuration of a semi-distributive GR model}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(airGRiwrm)
```


## Semi-distributive network description

List of nodes

```{r}
seine_nodes <- readr::read_delim(
  file = system.file("seine_data", "network_gauging_stations.txt", package = "airGRiwrm"),
  delim = "\t"
)
seine_nodes
```

Create the Griwrm object which lists the nodes and describes the network diagram. It's a dataframe of class `Griwrm` and `Griwrm` with specific column names:

- `id`: the identifier of the node in the network.
- `down`: the identifier of the next hydrological node downstream.
- `length`: hydraulic distance to the next hydrological downstream node.
- `model`: Name of the hydrological model used (E.g. "RunModel_GR4J"). `NA` for other type of node.
- `area`: Area of the sub-catchment (km<sup>2</sup>). Used for hydrological model such as GR models. `NA` if not used.

`Griwrm` function helps to rename the columns of the dataframe and assign the variable classes.

```{r}
seine_nodes$model <- "RunModel_GR4J"
# Generate the Griwrm object
griwrm <- Griwrm(seine_nodes, list(id = "id_sgl", down = "id_aval", length = "distance_aval"))
griwrm
```

The diagram of the network structure is represented below with in blue the upstream nodes with a GR4J model and in green the intermediate nodes with an SD (GR4J + LAG) model.

```{r fig.height = 7, fig.width = 8}
DiagramGriwrm(griwrm)
```



## Observation time series

Loading hydrometeorological data on the Seine river basin from the ClimAware project:

```{r, warning=FALSE, message=FALSE}

Precip <- NULL
PotEvap <- NULL
Qobs <- NULL

MergeTS <- function(dfOld, id, dfNew) {
    names(dfNew) <- c("DatesR", id) # Renaming columns of the new input into date and sub-basin ID
    if(is.null(dfOld)) {
    dfOut <- dfNew # Creation of the first column
  } else {
    dfOut <- merge(dfOld, dfNew, by = "DatesR", all = TRUE) # Merge the new columns respecting to date column
  }
  return(dfOut)
}

for(id in griwrm$id) {
  url <-
    file.path(
      "https://stratus.irstea.fr/d/0b18e688851a45478f7a/files/?p=/climaware_hydro/Q_OBS_NAT",
      paste0(id, "_NAT.txt&dl=1")
    )
  ts <- readr::read_delim(file = url,
                          delim = ";", skip = 16, trim_ws = TRUE)
  # Date conversion to POSIX
  ts$Date <- as.POSIXlt(lubridate::ymd(ts$Date))
  # Ptot column  is merged into Precip dataframe
  Precip <- MergeTS(Precip, id, ts[,c("Date", "Ptot")])
  # ETP column is merged into PotEvap dataframe
  PotEvap <- MergeTS(PotEvap, id, ts[,c("Date", "ETP")])
  # Convert Qobs from m3/s to mm/time step
  ts$Qnat <- ts$Qnat * 86.4 / griwrm$area[griwrm$id == id]
  # Setting data gaps to NA
  ts$Qnat[ts$Qnat <= 0] <- NA
  # Qnat column is merged into Qobs dataframe
  Qobs <- MergeTS(Qobs, id, ts[,c("Date", "Qnat")])
}
DatesR <- Precip$DatesR
Precip$DateR <- NULL
PotEvap$DateR <- NULL
Qobs$DateR <- NULL
```

## Generate the GRIWRM InputsModel object

The GRIWRM InputsModel object is a list of airGR InputsModel. The identifier of the sub-basin is used as key in the list which is ordered from upstream to downstream.

The airGR CreateInputsModel function is extended in order to handle the griwrm object which describe the basin diagram:


```{r}
InputsModel <- CreateInputsModel(griwrm, DatesR, Precip, PotEvap, Qobs)
```



## Save data for next vignettes

```{r}
dir.create("_cache", showWarnings = FALSE)
save(griwrm, Qobs, InputsModel, file = "_cache/V01.RData")
save(griwrm, DatesR, Precip, PotEvap, Qobs, MergeTS, file = "_cache/V01b.RData")
```

