---
title: "Running open-loop influenced semi-distributed flow model"
author: "David Dorchies"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Running open-loop influenced semi-distributed flow model}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(airGRiwrm)
library(DiagrammeR)
```

## Integration of the reservoir connections into the model

### Loading naturalised data

```{r}
load("_cache/V01b.RData")
```

### Add connections to the reservoirs in the gauging station network

Because of the airGR SD model structure, the topology of the network will difere between the physical one and the modelled one.

For example, the physical topology of the Aube lake is represented below:

```{r echo = FALSE, fig.height = 3}

mmd <- function(x, ...) {
  # For avoiding crash of R CMD build in console mode
  if(Sys.getenv("RSTUDIO") == "1") {
    mermaid(x, ...)
  }
}

mmd("graph LR
  TRANN_01 -->|1.5km| AUBE_P2
  AUBE_P2 -->|22km| AUBE_R3
  AUBE_P2 --> AUBE(AUBE)
  AUBE --> AUBE_R3
  AUBE_R3 -->|44.5km| ARCIS_24
style AUBE_P2 fill:#fcc
style AUBE_R3 fill:#fcc
style AUBE fill:#ccf
", width = "100%")
```

In the SD model, we do not model intermediate flows as well as the reservoir in the catchment. As a result, an equivalent topology compatible with airGR will be the one below:

```{r echo = FALSE}
mmd("
graph LR
TRANN_01 -->|68km| ARCIS_24
AUBE_P2 -->|66.5km| ARCIS_24
AUBE_R3 -->|44.5km| ARCIS_24
style AUBE_P2 fill:#fcc
style AUBE_R3 fill:#fcc
", width = "100%")
```

`AUBE_P2` will propagate negative flow to downstream (reservoir inflows) while `AUBE_R3` will propagate positive flow to downstream (reservoir releases).

Configuration on lake Seine is similar:

```{r echo = FALSE, fig.height = 3}
mmd("
graph LR
  BAR-S_06 -->|6km| SEINE_P7
  SEINE_P7 -->|32km| SEINE_R8
  SEINE_P7 --> SEINE(SEINE)
  SEINE--> SEINE_R8
  SEINE_R8 -->|41.7km| MERY-_22
  style SEINE_P7 fill:#fcc
  style SEINE_R8 fill:#fcc
  style SEINE fill:#ccf
", width = "100%")
```

which can be translate as:

```{r echo = FALSE}
mmd("
graph LR
  BAR-S_06 -->|79.7km| MERY-_22
  SEINE_P7 -->|73.7km| MERY-_22
  SEINE_R8 -->|41.7km| MERY-_22
  style SEINE_P7 fill:#fcc
  style SEINE_R8 fill:#fcc
", width = "100%")
```

Pannecière is an inline reservoir:

```{r echo = FALSE, fig.height = 2}
mmd("
graph LR
P(PANNECIERE)
CHAUM_07 -->|0km| P
P --> |153km| GURGY_02
style P fill:#ccf
", width = "100%")
```

It can be modelled as:

```{r echo = FALSE}
mmd("
graph LR
CHAUM_07 --> |153km| GURGY_02
PANNEC_P --> |153km| GURGY_02
PANNEC_R --> |153km| GURGY_02
style PANNEC_P fill:#fcc
style PANNEC_R fill:#fcc
", width = "100%")
```

With $Q_{PANNEC\_P} = - Q_{CHAUM\_07}$ as all the upstream flow fills the reservoir.

Marne lake can be mapped as:

```{r echo = FALSE}
mmd("
graph LR
LOUVE_19 -->|0.5km| MARNE_P28
MARNE_P23 -->|3km| STDIZ_04
MARNE_P23 --> M(MARNE)
MARNE_P28 --> M
MARNE_P28 -->|25.6km| MARNE_R25
M --> MARNE_R25
STDIZ_04 -->|28.7km| MARNE_R25
MARNE_R25 -->|56.9km| CHALO_21
style MARNE_P28 fill:#fcc
style MARNE_P23 fill:#fcc
style MARNE_R25 fill:#fcc
style M fill:#ccf
", width = "100%")
```
And can be modeled as:

```{r echo = FALSE}
mmd("
graph LR
MARNE_P23 -->|3km| STDIZ_04
LOUVE_19 -->|83km| CHALO_21
MARNE_P28 -->|82.5km| CHALO_21
STDIZ_04 -->|85.6km| CHALO_21
MARNE_R25 -->|56.9km| CHALO_21
style MARNE_P28 fill:#fcc
style MARNE_P23 fill:#fcc
style MARNE_R25 fill:#fcc
", width = "100%")
```

Hence the topological connection to the reservoirs is described in the model as below:

```{r}
reservoir_connections <- readr::read_delim(
  file = system.file("seine_data", "network_reservoir_connections.txt", package = "airGRiwrm"),
  delim = "\t"
)
reservoir_connections
```

Reservoir connections are added to the Griwrm object:

```{r}
reservoir_connections$model <- NA
reservoir_connections$area <- NA
griwrm2 <- rbind(griwrm, reservoir_connections)
DiagramGriwrm(griwrm2)
```


## Loading reservoir observation time series

Description of the files, the columns and the type of connection (inlet / outlet) are defined in the list below:

```{r}

lCfgReservoirs <- jsonlite::read_json(system.file("seine_data", "config_reservoirs.json", package = "airGRiwrm"))
str(lCfgReservoirs)
```

Then, we load observation data for each reservoir and each connection:

```{r}

for(reservoir_id in names(lCfgReservoirs)) {
  df <- readr::read_delim(
    file = file.path(
      "https://stratus.irstea.fr/d/0b18e688851a45478f7a/files/?p=/Reservoir_current_rules",
      paste0(lCfgReservoirs[[reservoir_id]]$file, "&dl=1")
    ),
    delim = "\t",
    col_types = readr::cols(
      Date = readr::col_character(),
      .default = readr::col_double()
    )
  )
  df$Date <- format(as.POSIXlt(lubridate::dmy(df$Date)), "%Y-%m-%d")
  Qreservoir <- merge(data.frame(Date = format(DatesR, "%Y-%m-%d")), df, by = "Date", all.x = TRUE)
  for(connect in names(lCfgReservoirs[[reservoir_id]]$connections)) {
    # Replace data gap by zeros (should be interpolated ?)
    Qreservoir[is.na(Qreservoir[,lCfgReservoirs[[reservoir_id]]$connections[[connect]]$col]),lCfgReservoirs[[reservoir_id]]$connections[[connect]]$col] <- 0
    if(lCfgReservoirs[[reservoir_id]]$connections[[connect]]$type == "in") {
      # Reservoir inlet flow is a withdrawal for the catchment: this is a negative flow to route
      Qreservoir[,lCfgReservoirs[[reservoir_id]]$connections[[connect]]$col] <- -Qreservoir[,lCfgReservoirs[[reservoir_id]]$connections[[connect]]$col]
    }
    Qobs <- cbind(
      Qobs,
      Qreservoir[,lCfgReservoirs[[reservoir_id]]$connections[[connect]]$col]
    )
    names(Qobs)[ncol(Qobs)] <- connect
  }
}
# Convert flows from m3/s to m3/day
Qobs[,-1] <- Qobs[,-1] * 86400

```

## How to handle online reservoir ? The Pannecière lake case.

There are two possibilities:

- truncate the system and only simulate the release of the reservoir if we only care about downstream flows
- add a fictive inlet to the reservoir that will store all upstream discharge into the reservoir

If we know in advance the flow released by the reservoir, upstream flow informations is not usefull for the simulation. But reservoir management simulation would need upstream flow informations for simulating the reservoir state during simulation. The second alternative will be useful for the next phases.

```{r}
Qobs$PANNEC_P <- -Qobs$CHAUM_07
```


## Create the InputsModel object

```{r}
InputsModel2 <- CreateInputsModel(griwrm2, DatesR, Precip, PotEvap, Qobs)
```

## Run simulation with naturalised flow parameters

### Load calibration parameters

```{r}
# Load RunOptions
load("_cache/V02.RData")
# Load calibrated parameters with Michel's method
load("_cache/V03.RData")
```


### How to handle former upstream sub-basins with upstream flows ?

A lag parameter is now mandatory for these sub-basins. As no calibration is possible at that stage an arbitrary one will be used.

```{r}
ParamMichel$STDIZ_04[5] <- 1
```


### Run simulation

```{r}
OutputsModels2 <- RunModel(
  InputsModel = InputsModel2,
  RunOptions = RunOptions,
  Param = ParamMichel
)
```

## Compare modelled flows with observed flows

### Load observed flow

```{r, warning=FALSE, message=FALSE}

Qobs2 <- NULL

# Files of observed flows doesn't exist for some basins
NatIds <- c("CHAUM_07", "MONTE_15", "NOGEN_13", "STGER_09", "TRANN_01")

ids <- griwrm$id[!griwrm$id %in% NatIds]

for(id in ids) {
  url <-
    file.path(
      "https://stratus.irstea.fr/d/0b18e688851a45478f7a/files/?p=/climaware_hydro/Q_OBS_NAT",
      paste0(id, "_BV.txt&dl=1")
    )
  ts <- readr::read_delim(file = url,
                          delim = ";", skip = 24, trim_ws = TRUE)
  # Date conversion to POSIX
  ts$Date <- as.POSIXlt(lubridate::ymd(ts$Date))
    # Convert Qobs from l/s to mm/time step
  ts$Q <- ts$Q * 86.4 / griwrm$area[griwrm$id == id] / 1000
  # Setting data gaps to NA
  ts$Q[ts$Q <= 0] <- NA
  # Column is merged into Qobs dataframe
  Qobs2 <- MergeTS(Qobs2, id, ts[,c("Date", "Q")])
}
```

## Save data for next vignettes
```{r}
ReduceOutputsModel <- function(OutputsModels, IndPeriod) {
  items <- names(OutputsModels)
  OutputsModelsOut <- sapply(items, function(x) {OutputsModels[[x]] <- OutputsModels[[x]][IndPeriod]})
  OutputsModelsOut$StateEnd <- OutputsModels$StateEnd
  class(OutputsModelsOut) <- class(OutputsModels)
  return(OutputsModelsOut)
}

QobsReservoirs <- Qobs[Qobs$DatesR < "2008-08-01",c("DatesR", reservoir_connections$id)]
save(QobsReservoirs, Qobs2, griwrm2, ReduceOutputsModel, file = "_cache/V04.RData")
```

### Comparison with simulated flows

```{r, fig.height = 5, fig.width = 8}
htmltools::tagList(lapply(
  ids,
  function(x) {
    Q2 <- Qobs2[RunOptions[[1]]$IndPeriod_Run,x]
    IndPeriod_Obs <- which(!is.na(Q2))
    OutputsModels <- ReduceOutputsModel(OutputsModels2[[x]], IndPeriod_Obs)
    plot(OutputsModels, Qobs = Q2[IndPeriod_Obs] , main = x)
  }
))
```



