---
title: "Severn_07: Combine tactical and operational planning management"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Severn_07: Combine tactical and operational planning management}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  comment = "#>",
  fig.width = 9,
  fig.asp = 0.68,
  out.width = "90%",
  fig.align = "center"
)
```

```{r setup-lib}
library(airGRiwrm)
library(lubridate)
```

# Introduction

Watershed-scale water resource management involves balancing ecological, social,
and economic needs through structured planning approaches.
**Tactical** and **operational** planning play distinct but complementary roles in
achieving sustainable water use, flood control, and ecosystem health.

*Tactical planning* in watershed management focuses on mid-term strategies, such as
infrastructure development, policy creation, and risk mitigation to ensure
sustainable water use over seasons or years.

*Operational planning* handles short-term, day-to-day activities such as water
allocation, reservoir release decisions, monitoring, and emergency response.

**airGRiwrm** offers various tools for introducing human influences into
catchment hydrological modelling, which can be combined to represent these
different planning levels. This vignette demonstrates how to integrate both
approaches in a single simulation workflow, using a reservoir (dam) project on
the Severn River as a case study.

# Study Case Presentation

## Project scenario

The example in this tutorial takes place on the Severn River in the United Kingdom.
The data is extracted from the CAMELS-GB database [Coxon et al. (2020)](https://doi.org/10.5285/8344E4F3-D2EA-44F5-8AFA-86D2987543A9),
which provides catchment attributes and hydro-meteorological timeseries for 671
catchments across Great Britain.

We consider a **reservoir (dam)** built directly on the river at gauging station "54095",
located upstream of gauge "54001".
The dam has one objective:

| Objective        | Description                                                        |
|------------------|----------------------------------------------------------------------|
| **Water supply** | Maintain a minimum daily release of 700,000 m3/day for downstream supply |

The reservoir is managed through two control layers:

| Planning Level   | Mechanism                  | Time Scale | Purpose                              |
|------------------|----------------------------|------------|--------------------------------------|
| **Operational**  | Filling curve (controller) | Daily      | Guide reservoir releases toward annual volume targets with constrained minimum release |
| **Tactical**     | Monthly restrictions       | Monthly    | Set release fraction based on reservoir volume relative to objective |

## How it works

1. **Storage mechanism**: Water flowing through gauging station "54095" enters the reservoir directly. The reservoir stores water according to an annual filling curve that defines target storage volumes throughout the year.

2. **Release mechanism**: The reservoir releases water downstream to node "54001". A PD controller computes the desired release rate to track the filling curve, then clamps it between a scaled minimum and a hard maximum. The minimum scales with the reservoir fill ratio.

3. **Tactical adjustment**: At each monthly step, the reservoir volume is assessed relative to the filling-curve objective. The ratio `release_fraction = min(1, V_current / V_objective)` is computed and stored, proportionally scaling the minimum allowed release for that month.

```{r load-data}
data(Severn)
Severn$BasinsInfo
```

# Network Setup

We construct a self-contained network from the `Severn` dataset. The network
includes two gauged stations (`54095` and `54001`) and a reservoir built
directly on the river at gauging station `54095`.

## Building the node table

```{r build-nodes}
# Extract base node information from Severn data
nodes_Severn <- Severn$BasinsInfo[, c(
  "gauge_id",
  "downstream_id",
  "distance_downstream",
  "area"
)]
names(nodes_Severn) <- c("id", "down", "length", "area")
nodes_Severn$model <- "RunModel_GR4J"

# Reduce to the two nodes of interest: 54095 (upstream) and 54001 (downstream)
nodes <- nodes_Severn[nodes_Severn$id %in% c("54095", "54001"), ]

# Node 54001 becomes the outlet -- no further downstream connection
nodes$down[nodes$id == "54001"] <- NA
nodes$length[nodes$id == "54001"] <- NA

# Add the Reservoir row: dam built directly on the river at 0 km downstream of 54095.
# The RunModel_GR4J row for 54095 now feeds into the Reservoir instead of 54001.
nodes <- rbind(
  nodes,
  data.frame(
    id = "Reservoir",
    down = "54001",
    length = 42,
    area = NA,
    model = "RunModel_Reservoir",
    stringsAsFactors = FALSE
  )
)

# Update 54095 to feed into the Reservoir (dam built at 0 km downstream)
nodes$down[nodes$id == "54095"] <- "Reservoir"
nodes$length[nodes$id == "54095"] <- 0

nodes
```

In this network:

- **"54095"** is the upstream gauged station where the dam/reservoir is built directly downstream. The GR4J model simulates the naturalized runoff here.
- **Reservoir** is the dam that stores water from the river and releases it downstream. It receives all flow from `54095` and releases to `54001`.
- **"54001"** is the downstream gauged station receiving the regulated release from the Reservoir.

## Creating the GRiwrm object

```{r create-griwrm}
griwrm <- CreateGRiwrm(nodes)
griwrm
```

## Visualising the network

```{r plot-network, fig.asp = 0.7}
plot(griwrm)
```

The diagram shows the upstream gauged node (`54095`), the reservoir (`Reservoir`)
built directly on the river, and the downstream gauged node (`54001`).
All flow from the catchment at `54095` passes through the reservoir before
reaching the outlet at `54001`.

# Base Simulation

Before introducing closed-loop control, we set up the meteorological inputs, model
parameters, and run a preliminary open-loop simulation to establish the reservoir's
initial state.

## Meteorological and observation data

```{r prepare-meteo}
BasinsObs <- Severn$BasinsObs
DatesR <- BasinsObs[[1]]$DatesR

PrecipTot <- cbind(sapply(BasinsObs, function(x) x$precipitation))
PotEvapTot <- cbind(sapply(BasinsObs, function(x) x$peti))
Qobs <- cbind(sapply(BasinsObs, function(x) x$discharge_spec))

# Convert to sub-catchment scale
Precip <- ConvertMeteoSD(griwrm, PrecipTot)
PotEvap <- ConvertMeteoSD(griwrm, PotEvapTot)
```

## Human influence inputs

We initialise the reservoir release time series to zero; the PD controller
will dynamically compute the release rate at each time step:

- **Qrelease (dam release):** Initialised to `1E15` for keeping the reservoir
  empty during warm-up simulation period — the controller will compute
  the release rate, clamped between a scaled minimum and a hard maximum
  (see Operational Control section below).

```{r prepare-quantities}
Qrelease <- data.frame(Reservoir = rep(1E15, length(DatesR)))
```

## Creating the InputsModel object

```{r create-inputs}
InputsModel <- suppressWarnings(
  CreateInputsModel(
    griwrm,
    DatesR,
    Precip,
    PotEvap,
    Qrelease = Qrelease
  )
)
str(InputsModel, max.level = 1)
```

## Run options and calibration parameters

We define a warm-up period covering the initial years of the dataset, followed by
a simulation period from 2000 to 2009. The full simulation will be extended month
by month in the time-loop section below.

```{r run-options}
IndPeriod_Run <- seq(
  which(format(InputsModel[[1]]$DatesR, format = "%Y-%m-%d") == "2002-01-01"),
  which(format(InputsModel[[1]]$DatesR, format = "%Y-%m-%d") == "2005-12-31")
)
IndPeriod_WarmUp <- seq(1, IndPeriod_Run[1] - 1)
```

Default (Michel) calibration parameters are provided for the gauged stations.
We also add a parameter set for the Reservoir: `c(Vmax, celerity)`, where
`Vmax = 100 × 10⁶ m³` is the maximum reservoir capacity and `celerity = 1`
is the inflow time-lag parameter.

```{r params}
Param <- list(
  `54095` = c(256.84415, 0.065046, 57.52368, 2.718095),
  `54001` = c(1.03, 24.77909, -1.904302, 21.75840, 1.378378),
  Reservoir = c(100E6, 1)
)
```

# Operational Control: The Filling Curve

## What is a filling curve?

A *filling curve* is a tactical-Operational planning tool used by reservoir
operators to define target storage volumes throughout the year. It typically
prescribes higher volumes during the dry season (to ensure water supply) and
lower volumes during the wet season (to reserve spillway capacity for flood
events).

## Defining the annual targets

We define a yearly filling curve that oscillates between 20 × 10⁶ m³ (winter
minimum) and 80 × 10⁶ m³ (summer maximum), staying within the reservoir capacity
of 100 × 10⁶ m³:

```{r filling-curve}
curve <- approx(
  x = c(31 * 11 - 365, 30 * 6, 31 * 11, 366 + 30 * 6),
  y = c(20E6, 80E6, 20E6, 80E6),
  xout = 1:366
)$y

# Visualise the filling curve
plot(
  1:366,
  curve / 1E6,
  type = "l",
  lwd = 2,
  xlab = "Day of Year",
  ylab = expression("Target Volume (10"^6 * " m"^3 * ")"),
  main = "Annual Filling Curve",
  col = "steelblue"
)
abline(h = 100, lty = 2, col = "red") # Vmax reference
abline(h = 80, lty = 3, col = "darkgreen")
abline(h = 20, lty = 3, col = "darkgreen")
legend(
  "topright",
  legend = c("Target curve", "Vmax = 100 hm3", "Operating band"),
  col = c("steelblue", "red", "darkgreen"),
  lty = c(1, 2, 3),
  lwd = c(2, 1, 1)
)
```

## The PD controller with hard constraints

A proportional-derivative (PD) controller compares the current reservoir volume to
the filling-curve target and computes a **release** command. The computed release
is then clamped between a minimum and maximum bound:

| Bound      | Value                                                        |
|------------|---------------------------------------------------------------------|
| **Maximum**  | `QrelMax` = 50 x 106 m3/day (physical release capacity)            |
| **Minimum**  | `release_fraction x QrelMin` where `QrelMin` = 700 x 103 m3/day   |

The key mechanism is the `release_fraction`, computed monthly by the tactical
layer as `min(1, V_current / V_objective)`. When the reservoir volume is below
the filling-curve target, the fraction is less than 1, proportionally reducing
the allowed minimum release. When the volume meets or exceeds the target,
the full mandatory minimum of 700,000 m3/day applies.

```{r controller-factory}
fn_filling_curve_factory <- function(sv, curve, QrelMax, QrelMin) {
  # Shared state across controller calls
  if (is.null(sv$state)) {
    sv$state <- list(prevError = 0, release_fraction = 1.0)
  }

  # PD gains
  Kp <- 1
  Kd <- 0.1

  function(Y) {
    Vsim <- Y[1] + Y[2] # Current simulated volume with inflows
    j <- as.numeric(format(sv$ts.date, "%j")) # Day of year
    Vobj_ts <- approx(x = 1:366, y = curve, xout = j)$y # Target for today

    error <- Vsim - Vobj_ts
    dError <- error - sv$state$prevError

    # Step 1: Compute Qrelease from PD controller
    ctrl_action <- Kp * error + Kd * dError
    sv$state$prevError <- error
    Qrelease <- ctrl_action

    # Step 2: Apply hard constraints -- clamp between scaled minimum and maximum
    frac <- sv$state$release_fraction
    cat(
      "Vsim:",
      Vsim / 1E6,
      "Vobj:",
      Vobj_ts / 1E6,
      "Error:",
      error / 1E6,
      "dError:",
      dError / 1E6,
      "CtrlAction:",
      ctrl_action / 1E6,
      "ReleaseFraction:",
      frac,
      "\n"
    )
    Qrelease <- max(frac * QrelMin, min(QrelMax, Qrelease))

    # Return a single-column matrix with the release command
    return(cbind(Qrelease))
  }
}
```

## Setting up the Supervisor

```{r supervisor}
sv <- CreateSupervisor(InputsModel)
```

Instantiate the controller function with the supervisor and filling curve:

```{r controller-fun}
fn_filling_curve <- fn_filling_curve_factory(
  sv = sv,
  curve = curve,
  QrelMax = 200 * 86400, # Maximum release rate (m3/day)
  QrelMin = 30 * 86400 # Mandatory minimum release rate (m3/day)
)
```

The factory pattern ensures the controller:

- Reads the current reservoir volume through `Y = "Reservoir$Vsim"`.
- Computes the PD control action based on the filling-curve error.
- Clamps the computed release between `release_fraction * QrelMin` and `QrelMax`.
- Returns a single-column matrix with the release command for `"Reservoir$Qrelease"`.
- Maintains internal state (previous error and release fraction) across time-steps.

Register the filling-curve controller with the supervisor:

```{r controller}
CreateController(
  sv,
  ctrl.id = "FillingCurve",
  Y = c("Reservoir$Vsim", "54095"), # Read current reservoir volume with inflows
  U = "Reservoir$Qrelease", # Release command only
  FUN = fn_filling_curve # PD control logic
)
```

# Tactical Management: Monthly Restrictions

## Volume-based restriction rule

In addition to the filling-curve controller, we implement a tactical rule: at the
start of each month, the ratio of the current reservoir volume to the
filling-curve objective volume is computed. This ratio, called `release_fraction`,
scales the minimum allowed release for the upcoming month.

The release fraction is computed as:

`release_fraction = min(1, V_current / V_objective)`

When `V_current < V_objective`, the fraction is less than 1, proportionally
reducing the minimum release below QrelMin (potentially to near zero when the
reservoir is nearly empty). When `V_current` meets or exceeds the objective,
the fraction is 1, so the full mandatory minimum of 700,000 m3/day applies.

The final daily release is then computed as:

`Qrelease = max(release_fraction * QrelMin,  min(QrelMax,  PD_controller_output))`

This ensures that when the reservoir is below target, both the controller output
and the minimum floor are reduced, allowing the reservoir to recover more quickly.

## Month-by-month time-loop simulation

The simulation runs in a time loop, processing one month at a time. At each
iteration:

1. The tactical restriction is checked and the release fraction is computed as
   `min(1, V_current / V_objective)`.
2. The controller determines the release rate at each daily time step, clamping
   the PD output between the scaled minimum and hard maximum.
3. The model advances through the month's time steps.

```{r time-loop}
# Define simulation period: from 01/01/2000 up to 31/12/2009
dfTS <- data.frame(
  DatesR = DatesR,
  yearmonth = format(DatesR, "%Y-%m")
)
tactical_months <- unique(dfTS$yearmonth[
  dfTS$yearmonth >= "2002-01" &
    dfTS$yearmonth <= "2005-12"
])

first_run <- TRUE

# Store the tactical release fraction; default to 1 (unrestricted)
release_fraction <- 1.0

for (ym in tactical_months) {
  message(sprintf("Processing period: %s", ym), appendLF = FALSE)

  # Extract the current month's indices
  ym_IndPeriod_Run <- which(dfTS$yearmonth == ym)

  if (first_run) {
    message(" -> Release fraction = 1.0 (initial run)")
    RunOptions <- CreateRunOptions(
      InputsModel,
      IndPeriod_WarmUp = IndPeriod_WarmUp,
      IndPeriod_Run = ym_IndPeriod_Run,
      IniStates = list(Reservoir = c("Reservoir.V" = 0)),
      warnings = FALSE
    )
    OM <- suppressMessages(
      RunModel(
        sv,
        RunOptions = RunOptions,
        Param = Param
      )
    )
    first_run <- FALSE
  } else {
    # --- Tactical rule: compute release fraction from volume ratio ---
    V_current <- OM$Reservoir$StateEnd$Reservoir$V

    # Get the day-of-year for the first day of this month
    first_day_ym <- as.Date(paste0(ym, "-01"))
    j_first <- as.numeric(format(first_day_ym, "%j"))
    V_objective <- approx(x = 1:366, y = curve, xout = j_first)$y

    # Compute the release fraction: ratio of current to objective volume
    # When V_current < V_objective, fraction < 1, reducing the minimum release
    # When V_current >= V_objective, fraction = 1, full minimum applies
    release_fraction <- min(1, V_current / V_objective)

    # Update the supervisor state so the controller reads the new fraction
    sv$state$release_fraction <- release_fraction

    message(sprintf(
      " -> Release fraction: %.2f (V_cur=%.1f, V_obj=%.1f)",
      release_fraction,
      V_current / 1E6,
      V_objective / 1E6
    ))

    # Run the model for the current month with supervisor control
    OM <- suppressWarnings(
      RunModel(
        OM,
        InputsModel = sv,
        RunOptions = RunOptions,
        IndPeriod_Run = ym_IndPeriod_Run
      )
    )
  }
}
```

# Results

## Reservoir volume tracking

We can visualise how the simulated reservoir volume follows (or deviates from) the
filling curve target over the simulation period:

```{r plot-results, fig.asp = 0.7}
# Expand the annual filling curve to cover the full simulation period
# by repeating it for each year
ydoys <- as.numeric(format(as.Date(OM[[1]]$DatesR), "%j"))
curve_full <- approx(x = 1:366, y = curve, xout = ydoys)$y
# Plot Reservoir volume, inflows, and release
plot(OM$Reservoir, Vobs = curve_full)
```

## Flow components at the downstream gauge

```{r plot-downstream, fig.asp = 0.6}
plot(attr(OM, "Qm3s"))
```

# Key Takeaways

This vignette demonstrated how **tactical** and **operational** planning layers
can be integrated in airGRiwrm through a dam/reservoir project:

| Planning Level   | Tool                               | Purpose                                                  |
|------------------|-------------------------------------|----------------------------------------------------------|
| **Tactical**     | Monthly release fraction            | Scale minimum release based on volume ratio to objective |
| **Operational**  | Filling curve (PD controller)       | Daily volume tracking with constrained release bounds    |

The `Supervisor` / `Controller` architecture in airGRiwrm provides a flexible
framework for implementing custom water management rules. Controllers can read
simulated states (flows, volumes, etc.) and adjust model inputs
(releases) at each time step, enabling realistic closed-loop
simulations of regulated water systems.

In this example, a single controller manages the dam release with a key design
feature: the release is clamped between a scaled minimum and a hard maximum.
The scaling factor (`release_fraction`) is computed monthly as
`min(1, V_current / V_objective)`. When the reservoir volume is below the
filling-curve target, both the controller's computed output and the minimum
floor are proportionally reduced, allowing the reservoir to recover faster.
When the volume meets or exceeds the target, the full release range
from QrelMin to QrelMax is available.

## Summary of the control workflow

1. The **base simulation** (initial run) sets up the reservoir from an empty
   starting state and provides the hydrological context.
2. The **operational controller** runs at every time step, comparing the current
   volume to the filling curve via a PD controller, then clamping the computed
   release between `release_fraction * QrelMin` and `QrelMax`.
3. The **tactical layer** interrupts the monthly cycle to compute
   `release_fraction = min(1, V_current / V_objective)`, storing it in the
   supervisor state for the controller to use during the month.
4. The combined control ensures both daily responsiveness (filling curve tracking)
   and mid-term sustainability (tactical volume-based restrictions), while
   adapting the minimum release to the actual reservoir state.

# References

Coxon, G., Addor, N., Bloomfield, J.P., Freer, J., Fry, M., Hannaford, J.,
Howden, N.J.K., Lane, R., Lewis, M., Robinson, E.L., Wagener, T. and Woods, R.
(2020). Catchment attributes and hydro-meteorological timeseries for 671
catchments across Great Britain (CAMELS-GB). NERC Environmental Information Data
Centre. \doi{10.5285/8344E4F3-D2EA-44F5-8AFA-86D2987543A9}
