---
title: "Severn_07: Combine tactical and operational planning management"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Severn_07: Combine tactical and operational planning management}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  comment = "#>",
  fig.width = 9,
  fig.asp = 0.68,
  out.width = "90%",
  fig.align = "center"
)
```

```{r setup-lib}
library(airGRiwrm)
library(lubridate)
```

# Introduction

Watershed-scale water resource management involves balancing ecological, social,
and economic needs through structured planning approaches.
**Tactical** and **operational** planning play distinct but complementary roles in
achieving sustainable water use, flood control, and ecosystem health.

*Tactical planning* in watershed management focuses on mid-term strategies, such as
infrastructure development, policy creation, and risk mitigation to ensure
sustainable water use over seasons or years.

*Operational planning* handles short-term, day-to-day activities such as water
allocation, reservoir release decisions, monitoring, and emergency response.

**airGRiwrm** offers various tools for introducing human influences into
catchment hydrological modelling, which can be combined to represent these
different planning levels. This vignette demonstrates how to integrate both
approaches in a single simulation workflow, using a derived reservoir project on
the Severn River as a case study.

# Study Case Presentation

## Project scenario

The example in this tutorial takes place on the Severn River in the United Kingdom.
The data is extracted from the CAMELS-GB database [Coxon et al. (2020)](https://doi.org/10.5285/8344E4F3-D2EA-44F5-8AFA-86D2987543A9),
which provides catchment attributes and hydro-meteorological timeseries for 671
catchments across Great Britain.

We consider a **derived reservoir project** located upstream of gauge "54001".
The project has two objectives:

| Objective            | Description                                                        |
|----------------------|----------------------------------------------------------------------|
| **Water supply**     | Store diverted water to meet demand at a withdrawal point nearby     |
| **Environmental flow** | Maintain minimum river flow at the diversion point for ecology    |

The reservoir is managed through two control layers:

| Planning Level   | Mechanism                  | Time Scale | Purpose                              |
|------------------|----------------------------|------------|--------------------------------------|
| **Operational**  | Filling curve (controller) | Daily      | Guide reservoir releases toward annual volume targets |
| **Tactical**     | Monthly restrictions       | Monthly    | Limit water supply withdrawals when reservoir is low |

## How it works

1. **Filling mechanism**: Water is diverted from the river at node "54095" and transferred to the reservoir ("Reservoir"). The diversion is limited by a minimum environmental flow requirement at the diversion point.

2. **Release mechanism**: The reservoir releases water back to the river at node "54001", guided by an annual filling curve that defines target storage volumes throughout the year.

3. **Tactical adjustment**: At each monthly step, the remaining reservoir volume is assessed and water supply withdrawals may be restricted if the reservoir approaches a depletion threshold.

```{r load-data}
data(Severn)
Severn$BasinsInfo
```

# Network Setup

We construct a self-contained network from the `Severn` dataset. The network
includes only two gauged stations (`54095` and `54001`), a diversion point,
a withdrawal node, and a reservoir.

## Building the node table

```{r build-nodes}
# Extract base node information from Severn data
nodes_Severn <- Severn$BasinsInfo[, c("gauge_id", "downstream_id",
                                      "distance_downstream", "area")]
names(nodes_Severn) <- c("id", "down", "length", "area")
nodes_Severn$model <- "RunModel_GR4J"

# Reduce to the two nodes of interest: 54095 (upstream) and 54001 (downstream)
n_derived_rsrvr <- nodes_Severn[nodes_Severn$id %in% c("54095", "54001"), ]

# Node 54001 becomes the outlet -- no further downstream connection
n_derived_rsrvr$down[n_derived_rsrvr$id == "54001"] <- NA
n_derived_rsrvr$length[n_derived_rsrvr$id == "54001"] <- NA

# Add a Diversion row for "54095" that extracts water and sends it to the Reservoir.
# The gauged RunModel_GR4J row of 54095 (above) keeps its original downstream
# connection to 54001, so non-diverted flow still reaches the outlet naturally.
# Add a Withdrawal (WD) node connected to the Reservoir for water supply abstraction.
n_derived_rsrvr <- rbind(
  n_derived_rsrvr,
  data.frame(
    id = c("54095", "Reservoir", "WD"),
    down = c("Reservoir", "54001", "Reservoir"),
    length = c(0, 42, 0),
    area = c(NA, NA, NA),
    model = c("Diversion", "RunModel_Reservoir", NA),
    stringsAsFactors = FALSE
  )
)

n_derived_rsrvr
```

In this network:

- **"54095"** is the upstream gauged station where water is diverted from the river.
- **Reservoir** is the reservoir that stores diverted water and releases it downstream.
- **WD** is the withdrawal node connected to the Reservoir, representing the water
  supply abstraction point located at the dam. The reservoir's first objective
  is securing water for this withdrawal point.
- **"54001"** is the downstream gauged station receiving both the residual flow
  from upstream via the Reservoir release.

## Creating the GRiwrm object

```{r create-griwrm}
griwrm <- CreateGRiwrm(n_derived_rsrvr)
griwrm
```

## Visualising the network

```{r plot-network, fig.asp = 0.7}
plot(griwrm)
```

The diagram shows the upstream gauged node (`54095`), the reservoir (`Reservoir`),
the withdrawal node (`WD`), and the downstream gauged node (`54001`).
Flow from the river at `54095` feeds into the reservoir, which supplies
the withdrawal point and releases water back at `54001`.

# Base Simulation

Before introducing closed-loop control, we set up the meteorological inputs, model
parameters, and run a preliminary open-loop simulation to establish the reservoir's
initial state.

## Meteorological and observation data

```{r prepare-meteo}
BasinsObs <- Severn$BasinsObs
DatesR <- BasinsObs[[1]]$DatesR

PrecipTot <- cbind(sapply(BasinsObs, function(x) x$precipitation))
PotEvapTot <- cbind(sapply(BasinsObs, function(x) x$peti))
Qobs <- cbind(sapply(BasinsObs, function(x) x$discharge_spec))

# Convert to sub-catchment scale
Precip <- ConvertMeteoSD(griwrm, PrecipTot)
PotEvap <- ConvertMeteoSD(griwrm, PotEvapTot)
```

## Human influence inputs

We initialise the diversion and release time series to zero; the PD controller
will dynamically set the diversion at node `54095` and the reservoir release
at each time step. Only the withdrawal at the `WD` node and the minimum
environmental flow at the diversion point remain as fixed inputs:

- **Qinf (diversion):** Initialised to `0` at node `54095` — the controller
  will compute the actual diversion rate to track the filling curve.
- **Qinf (withdrawal):** A constant withdrawal of 500 000 m³/day from the `WD`
  node, abstracting water from the Reservoir for water supply.
- **Qrelease (dam release):** Initialised to `0` — the controller will compute
  the release rate when the reservoir is above the filling-curve target.
- **Qmin (minimum flow):** A minimum environmental flow of 3 × 10⁶ m³/day must
  be maintained at the diversion point `54095`.

```{r prepare-quantities}
Qinf <- data.frame(
  `54095` = rep(0, length(DatesR)),
  WD = rep(-100E3, length(DatesR)),
  check.names = FALSE
)

Qrelease <- data.frame(Reservoir = rep(0, length(DatesR)))

Qmin <- data.frame(
  `54095` = rep(3E6, length(DatesR)),
  check.names = FALSE
)
```

## Creating the InputsModel object

```{r create-inputs}
InputsModel <- suppressWarnings(
  CreateInputsModel(
    griwrm,
    DatesR,
    Precip,
    PotEvap,
    Qinf = Qinf,
    Qrelease = Qrelease,
    Qmin = Qmin
  )
)
str(InputsModel, max.level = 1)
```

## Run options and calibration parameters

We define a warm-up period covering the initial years of the dataset, followed by
a simulation period from 1990 to 1999. The full simulation will be extended month
by month in the time-loop section below.

```{r run-options}
IndPeriod_Run <- seq(
  which(format(InputsModel[[1]]$DatesR, format = "%Y-%m-%d") == "2000-01-01"),
  which(format(InputsModel[[1]]$DatesR, format = "%Y-%m-%d") == "2009-12-31")
)
IndPeriod_WarmUp <- seq(1, IndPeriod_Run[1] - 1)
```

Default (Michel) calibration parameters are provided for the gauged stations.
We also add a parameter set for the Reservoir: `c(Vmax, celerity)`, where
`Vmax = 10 × 10⁶ m³` is the maximum reservoir capacity and `celerity = 1`
is the inflow time-lag parameter.

```{r params}
Param <- list(
  `54095` = c(256.84415, 0.065046, 57.52368, 2.718095),
  `54001` = c(1.03, 24.77909, -1.904302, 21.75840, 1.378378),
  Reservoir = c(100E6, 1)
)
```

# Operational Control: The Filling Curve

## What is a filling curve?

A *filling curve* is a tactical-Operational planning tool used by reservoir
operators to define target storage volumes throughout the year. It typically
prescribes higher volumes during the dry season (to ensure water supply) and
lower volumes during the wet season (to reserve spillway capacity for flood
events).

## Defining the annual targets

We define a yearly filling curve that oscillates between 20 × 10⁶ m³ (winter
| minimum) and 80 × 10⁶ m³ (summer maximum), staying within the reservoir capacity
of 100 × 10⁶ m³:

```{r filling-curve}
curve <- approx(
  x = c(31 * 11 - 365, 30 * 6, 31 * 11, 366 + 30 * 6),
  y = c(20E6, 80E6, 20E6, 80E6),
  xout = 1:366
)$y

# Visualise the filling curve
plot(1:366, curve / 1E6, type = "l", lwd = 2,
     xlab = "Day of Year",
     ylab = expression("Target Volume (10" ^ 6 * " m" ^ 3 * ")"),
     main = "Annual Filling Curve",
     col = "steelblue")
abline(h = 100, lty = 2, col = "red")  # Vmax reference
abline(h = 80, lty = 3, col = "darkgreen")
abline(h = 20, lty = 3, col = "darkgreen")
legend("topright",
       legend = c("Target curve", "Vmax = 100 hm³", "Operating band"),
       col = c("steelblue", "red", "darkgreen"),
       lty = c(1, 2, 3), lwd = c(2, 1, 1))
```

## The PD controller

A proportional-derivative (PD) controller compares the current reservoir volume to
the filling-curve target and drives **two** commands:

1. **Diversion** at node `"54095"` (`U[,"54095$Qdiv"]`) — used to fill the reservoir
   when the volume is below the filling-curve target.
2. **Release** from the `"Reservoir"` node (`U[,"Reservoir$Qrelease"]`) — used to
   drain the reservoir when the volume is above the target.

At every time step exactly one command is active (non-zero) and the other is set
to zero:

| Condition              | Diversion (`54095$Qdiv`) | Release (`Reservoir$Qrelease`) |
|------------------------|--------------------------|-------------------------------|
| Volume **below** target | Positive (filling rate)  | 0                             |
| Volume **above** target | 0                        | Positive (draining rate)      |

```{r controller-factory}
fn_filling_curve_factory <- function(sv, curve, QdivMax, QrelMax) {
  # Shared state across controller calls
  if (is.null(sv$state)) {
    sv$state <- list(prevError = 0)
  }

  # PD gains
  Kp <- 1
  Kd <- 1

  function(Y) {
    Vsim <- Y[1]  # Current simulated volume
    j <- as.numeric(format(sv$ts.date, "%j"))  # Day of year
    Vobj_ts <- approx(x = 1:366, y = curve, xout = j)$y  # Target for today

    error <- Vsim - Vobj_ts
    dError <- error - sv$state$prevError

    ctrl_action <- Kp * error + Kd * dError
    sv$state$prevError <- error

    if (error > 0) {
      # Reservoir above target -> release water, diversion off
      Qrel <- max(0, min(QrelMax, ctrl_action))
      Qdiv <- 0
    } else {
      # Reservoir below target -> divert water, release off
      Qdiv <- -max(0, min(QdivMax, -ctrl_action))
      Qrel <- 0
    }

    # Return a two-column matrix: [Qdiv, Qrelease]
    return(cbind(Qdiv, Qrel))
  }
}
```

## Setting up the Supervisor

```{r supervisor}
sv <- CreateSupervisor(InputsModel)
```

Instantiate the controller function with the supervisor and filling curve:

```{r controller-fun}
fn_filling_curve <- fn_filling_curve_factory(
  sv = sv,
  curve = curve,
  QdivMax = 10E6,   # Maximum diversion rate (m³/day)
  QrelMax = 500E3   # Maximum release rate (m³/day)
)
```

The factory pattern ensures the controller:

- Reads the current reservoir volume through `Y = "Reservoir$Vsim"`.
- Computes the PD control action and decides whether to divert or release.
- Returns a two-column matrix with columns for `"54095$Qdiv"` and
  `"Reservoir$Qrelease"`, so that exactly one command is active per step.
- Maintains internal state (previous error) across time-steps.

Register the filling-curve controller with the supervisor:

```{r controller}
CreateController(
  sv,
  ctrl.id = "FillingCurve",
  Y = "Reservoir$Vsim",                        # Read current reservoir volume
  U = c("54095$Qdiv", "Reservoir$Qrelease"),   # Diversion and release commands
  FUN = fn_filling_curve                       # PD control logic
)
```

# Tactical Management: Monthly Restrictions

## Diversion restriction rule

In addition to the filling-curve controller, we implement a tactical rule: at the start of each
month, if the remaining reservoir volume would last less than 90 days at the current
net outflow rate, the **maximum diversion rate** of the controller is reduced by 50%
to prevent rapid depletion.

## Month-by-month time-loop simulation

The simulation runs in a time loop, processing one month at a time. At each
iteration:

1. The tactical restriction is checked and the controller's diversion limit is
   adjusted if needed.
2. The controller determines whether to divert or release at each daily time step
   to track the filling curve.
3. The model advances through the month's time steps.

```{r time-loop}
# Define simulation period: from 01/01/2000 up to 31/12/2009
dfTS <- data.frame(
  DatesR = DatesR,
  yearmonth = format(DatesR, "%Y-%m")
)
tactical_months <- unique(dfTS$yearmonth[dfTS$yearmonth >= "2000-01" &
                                        dfTS$yearmonth <= "2009-12"])

first_run <- TRUE

for (ym in tactical_months) {
  message(sprintf("Processing period: %s", ym), appendLF = FALSE)

  # Extract the current month's indices
  ym_IndPeriod_Run <- which(dfTS$yearmonth == ym)

  if (first_run) {
    RunOptions <- CreateRunOptions(
      InputsModel,
      IndPeriod_WarmUp = IndPeriod_WarmUp,
      IndPeriod_Run = ym_IndPeriod_Run,
      warnings = FALSE
    )
    OM <- RunModel(
      sv,
      RunOptions = RunOptions,
      Param = Param
    )
    first_run <- FALSE
  } else {
    # --- Tactical rule: check depletion risk ---
    Q_WD <- Qinf$WD[ym_IndPeriod_Run]

    current_volume_variation <- max(
      0,
      OM$Reservoir$Vsim[length(OM$Reservoir$Vsim)-1] - OM$Reservoir$Vsim[length(OM$Reservoir$Vsim)])
    V_current <- OM$Reservoir$StateEnd$Reservoir$V

    nb_remain_days <- V_current / current_volume_variation

    if (nb_remain_days < 90) {
      # Reduce the withdrawals by 50%
      Q_WD <- Q_WD * 0.5
      message(sprintf("  -> Diversion restricted (remaining: %.1f days)", nb_remain_days))
    } else {
      message(sprintf("  -> Diversion unrestricted (remaining: %.1f days)", nb_remain_days))
    }

    # Run the model for the current month with supervisor control
    OM <- suppressWarnings(
      RunModel(
        OM,
        InputsModel = sv,
        RunOptions = RunOptions,
        IndPeriod_Run = ym_IndPeriod_Run,
        Qinf = data.frame(WD = Q_WD)
      )
    )
  }
}
```

# Results

## Reservoir volume tracking

We can visualise how the simulated reservoir volume follows (or deviates from) the
filling curve target over the simulation period:

```{r plot-results, fig.asp = 0.7}
# Extract simulated reservoir volumes
Vsim <- OM$Reservoir$Vsim
sim_dates <- as.Date(OM[[1]]$DatesR)

# Expand the annual filling curve to cover the full simulation period
# by repeating it for each year
ydoys <- as.numeric(format(sim_dates, "%j"))
curve_full <- approx(x = 1:366, y = curve, xout = ydoys)$y

par(mar = c(5, 4, 2, 2) + 0.1)

plot(sim_dates, Vsim / 1E6, type = "l", lwd = 1.5, col = "darkgreen",
     xlab = "",
     ylab = expression("Volume (10" ^ 6 * " m" ^ 3 * ")"),
     main = "Simulated Reservoir Volume",
     xaxt = "n")

# X-axis ticks every 3 months with horizontal labels
at_dates <- seq(min(sim_dates), max(sim_dates), by = "3 months")
axis.Date(1, at = at_dates, format = "%Y-%m", cex.axis = 0.8)

# Overlay the filling curve target
lines(sim_dates, curve_full / 1E6, col = "steelblue", lwd = 2, lty = 2)
abline(h = 10, lty = 3, col = "red")  # Vmax reference

legend("topright",
       legend = c("Simulated volume", "Filling curve target",
                  "Vmax = 10×10⁶ m³"),
       col = c("darkgreen", "steelblue", "red"),
       lty = c(1, 2, 3), lwd = c(1.5, 2, 1))
```

## Flow components at the downstream gauge

```{r plot-downstream, fig.asp = 0.6}
sim_dates <- as.Date(OM[[1]]$DatesR)

# Flow at 54001 (downstream outlet)
Q_downstream <- OM[["54001"]]$Qsim_m3

# Flow at 54095: before diversion (naturalized) = Qsim_m3 + Qdiv_m3
Q_54095_before <- OM[["54095"]]$Qsim_m3 + OM[["54095"]]$Qdiv_m3

# Flow at 54095: after diversion (river flow remaining)
Q_54095_after <- OM[["54095"]]$Qsim_m3

par(mar = c(5, 4, 2, 2) + 0.1)

plot(sim_dates, Q_downstream / 1E6, type = "l", lwd = 1, col = "navy",
     xlab = "",
     ylab = expression("Discharge (10" ^ 6 * " m" ^ 3 * "/day)"),
     main = "Downstream and Diversion Point Flows",
     xaxt = "n",
     ylim = range(c(Q_downstream, Q_54095_before, Q_54095_after) / 1E6, na.rm = TRUE))

# X-axis ticks every 3 months with horizontal labels
at_dates <- seq(min(sim_dates), max(sim_dates), by = "3 months")
axis.Date(1, at = at_dates, format = "%Y-%m", cex.axis = 0.8)

# Add flow at 54095 before diversion (naturalized)
lines(sim_dates, Q_54095_before / 1E6, col = "orange", lwd = 1)

# Add flow at 54095 after diversion
lines(sim_dates, Q_54095_after / 1E6, col = "forestgreen", lwd = 1)

abline(h = 0, lty = 3, col = "grey")

legend("topright",
       legend = c("Flow at 54001 (downstream)",
                  "Flow at 54095 before diversion",
                  "Flow at 54095 after diversion"),
       col = c("navy", "orange", "forestgreen"),
       lwd = 1)
```

# Key Takeaways

This vignette demonstrated how **tactical** and **operational** planning layers
can be integrated in airGRiwrm through a derived reservoir project:

| Planning Level   | Tool                          | Purpose                                                  |
|------------------|-------------------------------|----------------------------------------------------------|
| **Tactical**     | Monthly diversion restriction | Mid-term safeguard against reservoir depletion            |
| **Operational**  | Filling curve (PD controller) | Daily volume tracking to maintain annual storage targets |

The `Supervisor` / `Controller` architecture in airGRiwrm provides a flexible
framework for implementing custom water management rules. Controllers can read
simulated states (flows, volumes, etc.) and adjust multiple model inputs
(diversions, releases, withdrawals) at each time step, enabling realistic closed-loop
simulations of regulated water systems.

In this example, a single controller drives **two commands** simultaneously:
diversion into the reservoir and release from the reservoir.  At each time step,
the controller decides which lever to act on based on the sign of the filling-curve
error, ensuring that only one action is active at a time.

## Summary of the control workflow

1. The **base simulation** (initial run) sets up the reservoir from an empty
   starting state and provides the hydrological context.
2. The **operational controller** runs at every time step, comparing the current
   volume to the filling curve and deciding whether to divert (when below target)
   or release (when above target).
3. The **tactical layer** interrupts the monthly cycle to assess reservoir status
   and reduces the controller's maximum diversion rate if the water level is
   critically low.
4. The combined control ensures both daily responsiveness and mid-term
   sustainability.

# References

Coxon, G., Addor, N., Bloomfield, J.P., Freer, J., Fry, M., Hannaford, J.,
Howden, N.J.K., Lane, R., Lewis, M., Robinson, E.L., Wagener, T. and Woods, R.
(2020). Catchment attributes and hydro-meteorological timeseries for 671
catchments across Great Britain (CAMELS-GB). NERC Environmental Information Data
Centre. \doi{10.5285/8344E4F3-D2EA-44F5-8AFA-86D2987543A9}
