---
title: "Severn_07: Combine tactical and operational planning management"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Severn_07: Combine tactical and operational planning management}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  comment = "#>",
  fig.width = 6,
  fig.asp = 0.68,
  out.width = "70%",
  fig.align = "center"
)
```

Watershed-scale water resource management involves balancing ecological, social, 
and economic needs through structured planning approaches. 
Tactical and operational planning play distinct but complementary roles in 
achieving sustainable water use, flood control, and ecosystem health.
Tactical planning in watershed management focuses on mid-term strategies like 
infrastructure development, policy creation, and risk mitigation to ensure 
sustainable water use. 
Operational planning handles short-term, day-to-day activities such as water 
allocation, monitoring, and emergency response. 

**airGRiwrm** offers various tools for introducing human influences into 
catchment hydrological modelling, which can be combined to represent these 
different planning levels.

```{r setup}
library(airGRiwrm)
```

## Introducing time loop simulation

```{r}
# Setup model
griwrm <- CreateGRiwrm(rbind(
  n_derived_rsrvr,
  data.frame(
    id = "WD",
    down = "Dam",
    length = 0,
    area = NA,
    model = NA
  )
))
data(Severn)
DatesR <-  Severn$BasinsObs[[1]]$DatesR
Qinf <- data.frame(
  # Diversion to the dam
  `54095` = rep(-1E6, length(DatesR)),
  # Withdrawal in the dam
  WD = rep(-250000, length(DatesR))
)
names(Qinf)[1] <- "54095"
# Release of the dam back to the river
Qrelease <- data.frame(Dam = rep(100E3, length(DatesR)))
# Diversion limited by fixed minimum flow to let in the river
Qmin <- data.frame("54095" = rep(3E6, length(DatesR)))
names(Qmin) <- "54095"
e <- setupRunModel(
  runRunModel = FALSE,
  griwrm = griwrm,
  Qinf = Qinf,
  Qrelease = Qrelease,
  Qmin = Qmin
)
for (x in ls(e)) assign(x, get(x, e))

# Simulation periods up to 31/12/1986
dfTS <- data.frame(
  DatesR = DatesR,
  yearmonth = format(DatesR, "%Y-%m")
)
dfTS <- dfTS[1:(which(dfTS$yearmonth == "1987-01")[1] - 1), ]

# Set up initial conditions
ROO <- CreateRunOptions(InputsModel, IndPeriod_WarmUp = 1:364, IndPeriod_Run = 365L)
OM <- RunModel(InputsModel, ROO, Param)
```

## Combining time loop simulation and supervisor



```{r}
  sv <- CreateSupervisor(InputsModel)

  curve <- approx(x = c(31*11 - 365, 30 * 6, 31 * 11, 366 + 30 * 6),
                  y = c(20E6, 90E6, 20E6, 90E6),
                  xout = 1:366)$y

  fn_guide_curve_factory <- function(sv, curve) {
    function(y) {
      # How much to release for reaching the filling curve ?
      deltaV <- sv$OutputsModel$Dam$Vsim - curve[lubridate::yday(sv$ts.date)]
      # Minimum 500L/s and max 1E6 m3
      return(max(86400 / 2, min(1E6, deltaV)))
    }
  }
  fn_guide_curve <- fn_guide_curve_factory(sv, curve)

  CreateController(sv, "dam_filling_curve",
                   Y = NULL,
                   U = "Dam",
                   fn_guide_curve)

  for(ym in unique(dfTS$yearmonth[dfTS$DatesR > OM[[1]]$DatesR])) {
    message("Processing period ", ym)
    # Preparing extract of Qinf for the current run
    ym_IndPeriod_Run <- which(dfTS$yearmonth == ym)
    ym_Qinf <- Qinf[ym_IndPeriod_Run, , drop = FALSE]
    ym_Qrelease <- Qrelease[ym_IndPeriod_Run, , drop = FALSE]

    # 50% Restriction on reservoir withdrawals if remaining less than 90 days of water
    nb_remain_days <- OM$Dam$StateEnd$Reservoir$V / (-ym_Qinf$`WD`[1] + ym_Qrelease$Dam[1])
    if (nb_remain_days < 180) {
      ym_Qinf$`WD` <- -(max(0, OM$Dam$StateEnd$Reservoir$V - sum(ym_Qrelease$Dam))) / 365
    }
    OM <- RunModel(OM,
                   InputsModel = sv,
                   RunOptions = RunOptions,
                   IndPeriod_Run = ym_IndPeriod_Run,
                   Qinf = ym_Qinf)
  }
```